---
title: "CHOP weights-13 unique strata"
author: "Ilmul Jahan Tani"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
library(readxl)
library(DataExplorer)
library(tidyverse)
library(MASS)
library(gtsummary)
library(ggplot2)
library(dplyr)
library(car)
library(AUC)
library(pROC)
library(DescTools)
library(labelled)
library(knitr)
library(flextable)
```

```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
dat <- read_excel("C:/Users/ilmul/Documents/UMICH/RA works/CHOP Nonresponse weights Winter 2024/Response_outcomes_EDtelehealthR56_2023.12.27.xlsx")
```

```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
#Creating a dataframe with only the RESPONDERS (Response indicator = Yes)
datA <- dat %>% 
  filter(Response_indicator == 1)
```


```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
summary(dat)
```

```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
#selecting variables
dat2 <- dat %>% 
          dplyr::select(-rural_status, -discharge, -risk_assessment, -sb_plan)
```


```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
#converting the variables to factor
dat2$stratum_5_categories <- as.factor(dat2$stratum_5_categories)
dat2$ed_volume_category <- as.factor(dat2$ed_volume_category)
dat2$hospital_ownership <- as.factor(dat2$hospital_ownership)
dat2$psyemhos <- as.factor(dat2$psyemhos)
dat2$mapp18 <- as.factor(dat2$mapp18)
dat2$teach_hosp <- as.factor(dat2$teach_hosp)
dat2$Response_indicator <- as.factor(dat2$Response_indicator)
```

```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
#handling missing data
dat2$psyemhos2 <- ifelse(dat$psyemhos %in% c(1:2), dat$psyemhos, NA)

#dat2$psyemhos2 <- ifelse(dat2$psyemhos %in% c(1:2), dat2$psyemhos, "Unknown") # recoding missing to unknown
dat2$psyemhos2 <- as.factor(dat2$psyemhos2) # converting to factor

dat$mapp18 <- ifelse(dat$mapp18 %in% c(1:2), dat$mapp18, NA)

dat$teach_hosp <- ifelse(dat$teach_hosp %in% c(1:2), dat$teach_hosp, NA)



#selecting the final variables
dat3 <- dat2 %>% 
          dplyr::select(-psyemhos)
```

```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
table(dat3$ed_volume_category)

dat3$ed_volume_category2 <- car::Recode(dat3$ed_volume_category, recodes="1='small'; 2='medium'; 3='large'; else=NA",
                      levels = c('small', 'medium', 'large'), as.factor=T)

table(dat3$ed_volume_category2)
```

```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
table(dat3$hospital_ownership)

dat3$hospital_ownership2 <- car::Recode(dat3$hospital_ownership, recodes = "12='State'; 13='County'; 14='City'; 15='City-county'; 16='Hospital district or authority'; 21='Church-operated'; 23='Other not-for-profit'; 31='Individual investor-owned'; 32='Partnership investor owned'; 33='Corporation'; else=NA",
                      levels = c('State', 'County', 'City', 'City-county', 'Hospital district or authority', 'Church-operated', 'Other not-for-profit', 'Individual investor-owned', 'Partnership investor owned', 'Corporation'), as.factor=T)

table(dat3$hospital_ownership2)
```

```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
table(dat3$mapp18)

dat3$mapp182 <- car::Recode(dat3$mapp18, recodes = "1='Yes'; 2='No'; else=NA",
                      levels = c('Yes', 'No'), as.factor=T)

table(dat3$mapp182)
```

```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
table(dat3$teach_hosp)

dat3$teach_hosp2 <- car::Recode(dat3$teach_hosp, recodes = "1='Yes'; 2='No';  else=NA",
                      levels = c('Yes', 'No'), as.factor=T)

table(dat3$teach_hosp2)
```

```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
table(dat3$psyemhos2)

dat3$psyemhos2a <- car::Recode(dat3$psyemhos2, recodes = "1='Yes'; 2='No'; NA='Unknown'; else=NA",
                      levels = c('Yes', 'No', 'Unknown'), as.factor=T)

table(dat3$psyemhos2a)
```

```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
table(dat3$Response_indicator)

dat3$Response_indicator2 <- car::Recode(dat3$Response_indicator, recodes = "0='No'; 1='Yes'; else=NA",
                      levels = c('No', 'Yes'), as.factor=T)

table(dat3$Response_indicator2)
```

```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
dat4 <- dat3 %>% 
          dplyr::select(sample_id, aha_id, stratum_5_categories, ed_volume_category2, total_hospital_beds, hospital_ownership2, mapp182, psyemhos2a, teach_hosp2, Response_indicator2)
```


```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
summary(dat4)
```


```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
mod1 <- glm(Response_indicator2 ~ factor(stratum_5_categories), data = dat4, family = 'binomial')

summary(mod1)
# 3 Stratum categories are Significant
```

```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
mod2 <- glm(Response_indicator2 ~ factor(ed_volume_category2), data = dat4, family = 'binomial')

summary(mod2)
#All levels are significant
```

```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
mod3 <- glm(Response_indicator2 ~ total_hospital_beds, data = dat4, family = 'binomial')

summary(mod3)
#significant
```

```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
mod4 <- glm(Response_indicator2 ~ factor(hospital_ownership2), data = dat4, family = 'binomial')

summary(mod4)
#None are significant
```

```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
mod5 <- glm(Response_indicator2 ~ factor(psyemhos2a), data = dat4, family = 'binomial')

summary(mod5)
#Not significant
```

```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
mod6 <- glm(Response_indicator2 ~ factor(mapp182), data = dat4, family = 'binomial')

summary(mod6)
# Level 2 (Yes) is Significant
```

```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
mod7 <- glm(Response_indicator2 ~ factor(teach_hosp2), data = dat4, family = 'binomial')

summary(mod7)
#not significant
```

```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
mod_full <- glm(Response_indicator2 ~ factor(stratum_5_categories) + factor(ed_volume_category2) + total_hospital_beds + factor(hospital_ownership2) + factor(psyemhos2a) + factor(mapp182) + factor(teach_hosp2), data = dat4, family = 'binomial')

summary(mod_full)

#Stratum Northeast non-rural, West non-rural are significant
#ED_volume category3 (large) is marginally significant 
```

```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
#model with significant results only
mod_full_sig <- glm(Response_indicator2 ~ factor(stratum_5_categories) + factor(ed_volume_category2), data = dat4, family = 'binomial')

summary(mod_full_sig)
#Two of the levels of stratum variable are not significant
##All Ed_volume cat are significant
```

```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
#model with significant results and mapp18
mod_full_map <- glm(Response_indicator2 ~ factor(stratum_5_categories) + factor(ed_volume_category2) + factor(mapp182), data = dat4, family = 'binomial')

summary(mod_full_map)
#Some of the levels of stratum variable are significant
#Ed volume is marginally significant
```


```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
# **Classification tree**
library(foreign)
library(partykit)
```

```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
resp.tree <- ctree(factor(Response_indicator2) ~ factor(stratum_5_categories) + factor(ed_volume_category2) + total_hospital_beds + factor(hospital_ownership2) + factor(psyemhos2a) + factor(mapp182) + factor(teach_hosp2), data = dat4)

print(resp.tree)
```

```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
n.control <- ctree_control(minsplit=100, minbucket=100)
```

```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE, fig.show='hide'}
resp.tree <- ctree(factor(Response_indicator2) ~ factor(stratum_5_categories) + factor(ed_volume_category2) + total_hospital_beds + factor(hospital_ownership2) + factor(psyemhos2a) + factor(mapp182) + factor(teach_hosp2), data = dat4, control = n.control)

print(resp.tree)
plot(resp.tree)
```

```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE, fig.show='hide'}
set.seed(2024)
smp_size = floor(0.8 * nrow(dat4))
train_ind = sample(seq_len(nrow(dat4)), size = smp_size)
train = dat4[train_ind, ]
val = dat4[-train_ind, ] 
val = val[complete.cases(val), ]

ttree <- ctree(factor(Response_indicator2) ~ factor(stratum_5_categories) + factor(ed_volume_category2) + total_hospital_beds + factor(hospital_ownership2) + factor(psyemhos2a) + factor(mapp182) + factor(teach_hosp2), data = train)

print(ttree)
plot(ttree)
```

```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
library(crossval)

val$pred <- predict(ttree, val[, -which(names(val) =="Response_indicator2")]) # taking out DV

cm <- confusionMatrix(factor(val$Response_indicator2), factor(val$pred), negative="0")
cm

diagnosticErrors(cm)
```


```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE, fig.show='hide'}
#*Comparing AUC values of the classification tree and an interim logistic model**

#with full model
dat4$phat <- predict(mod_full, dat4, type = "response")
roc <- roc(factor(dat4$Response_indicator2), dat4$phat, plot=TRUE, auc.print=TRUE)

PseudoR2(mod_full, which="all")

#with model with significant only
dat4$phat1 <- predict(mod_full_sig, dat4, type = "response")
roc1 <- roc(factor(dat4$Response_indicator2), dat4$phat1, plot=TRUE, auc.print=TRUE)
roc1

auc(roc1)

PseudoR2(mod_full_sig, which="all")

#with model having significant results and mapp18
dat4$phat2 <- predict(mod_full_map, dat4, type = "response")
roc2 <- roc(factor(dat4$Response_indicator2), dat4$phat2, plot=TRUE, auc.print=TRUE)

PseudoR2(mod_full_map, which="all")
```

```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE, fig.show='hide'}
#trying a different way to plot AUC with value
# library(ROCR)
# 
# # Create prediction object
# m1.prediction <- prediction(dat4$phat, dat4$Response_indicator2)
# 
# # Calculate AUC value
# m1.auc <- performance(m1.prediction, "auc")@y.values[[1]]
# m1.auc
# 
# # Plot ROC curve
# m1.perf <- performance(m1.prediction, "tpr", "fpr")
# plot(m1.perf, main = "ROC Curve", col = "blue", lwd = 2)
# abline(a = 0, b = 1, lty = 2, lwd = 2)
# legend("bottomright", legend = paste("AUC = ", round(m1.auc, 2)), col = "blue", lwd = 2, bty = "n")
```



```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
#**Comparing AUC values for ctree with mapp18 only and model with significant predictors only

#Fitting the ctree model using only "mapp18" as the predictor
resp.tree1 <- ctree(factor(Response_indicator2) ~ factor(mapp182), data = dat4, control = n.control)
resp.tree1

pred_prob_ctree <- predict(resp.tree1, type = "prob")[, 2]
pred_prob_ctree
```

```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
roc_ctree <- roc(dat4$Response_indicator2, pred_prob_ctree)

auc_ctree <- auc(roc_ctree)
auc_ctree
```

```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
#getting auc values
roc_final <- roc(dat4$Response_indicator2, dat4$phat1) #taking phat1 from above
roc_final

auc_final <- auc(roc1) #taking roc1 from above
auc_final 
```

```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
#comparing the two auc values
comparison_table <- data.frame(
  Model = c("resp.ctree1", "mod_full_sig"),
  AUC = c(auc_ctree, auc_final)
)

ct <- print(comparison_table)

#AUC for ctree is 0.551
#AUC for model with sig preds only is 0.592
```

```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
kable(ct)
```


```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
#comparing vif
vif(mod_full)
vif(mod_full_sig)
```

```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
mod_ed <- glm(Response_indicator2 ~ factor(stratum_5_categories) + total_hospital_beds + factor(hospital_ownership2) + factor(psyemhos2a) + factor(mapp182) + factor(teach_hosp2), data = dat4, family = 'binomial')

summary(mod_ed)
```

```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
mod_ed_bed <- glm(Response_indicator2 ~ factor(stratum_5_categories) + factor(hospital_ownership2) + factor(psyemhos2a) + factor(mapp182) + factor(teach_hosp2), data = dat4, family = 'binomial')

summary(mod_ed_bed)
```


```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
#hospital_ownership
tbl_cross(dat4, row = hospital_ownership2, col = Response_indicator2, percent = "row")
```


```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
dat4 <- dat4 %>%
  mutate(new_hosp_ownership = case_when(
    hospital_ownership2 %in% c('City', 'City-county') ~ 'City combined',
    hospital_ownership2 %in% c('Individual investor-owned', 'Partnership investor owned') ~ 'Investor-owned',
    TRUE ~ hospital_ownership2
  ))
```


```{r, warning=FALSE, echo=FALSE, results='hide',message=FALSE}

#*Final logistic model
  
mod_new <- glm(Response_indicator2 ~ factor(stratum_5_categories) + factor(new_hosp_ownership) + factor(psyemhos2a) + factor(mapp182) + factor(teach_hosp2), data = dat4, family = 'binomial')

summary(mod_new)
```

```{r}
library(flextable)
r <- tbl_regression(mod_new, exp = T) %>% 
  bold_p() %>% 
  as_flex_table()
r
```

```{r}
save_as_docx(r, path = "C:/Users/ilmul/Documents/UMICH/RA works/CHOP Nonresponse weights Winter 2024/final model.docx")
```


```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
vif(mod_new)
```


```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
#Goodness of fit using AIC**

AIC(mod_new)
BIC(mod_new)
```


```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
#Comparing AUC values of the final model and classification tree**

#Fitting the ctree model using only "mapp18" as the predictor
resp.tree2 <- ctree(factor(Response_indicator2) ~ factor(stratum_5_categories) + factor(new_hosp_ownership) + factor(psyemhos2a) + factor(mapp182) + factor(teach_hosp2), data = dat4, control = n.control)
resp.tree2

pred_prob_ctree2 <- predict(resp.tree2, type = "prob")[, 2]
pred_prob_ctree2
```

```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
roc_ctree1 <- roc(dat4$Response_indicator2, pred_prob_ctree)

auc_ctree1 <- auc(roc_ctree1)
auc_ctree1
```

```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
dat4$phat2 <- predict(mod_new, dat4, type = "response")
#getting auc values
roc_final2 <- roc(dat4$Response_indicator2, dat4$phat2)
roc_final2

auc_final1 <- auc(roc_final2)
auc_final1 
```

```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
#comparing the two auc values
comparison_table1 <- data.frame(
  Model = c("resp.ctree2", "mod_new"),
  AUC = c(auc_ctree1, auc_final1)
)

ct1 <- print(comparison_table1)

#AUC for ctree is 0.551
#AUC for model with sig preds only is 0.597, earlier it was 0.592
```

```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
vif(mod_new)
```

```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
#comparing the two auc values
comparison_table2 <- data.frame(
  Model = c("resp.ctree", "mod_new"),
  AUC = c(auc_ctree1, auc_final1)
)

ct2 <- print(comparison_table2)

#AUC for ctree is 0.551
#AUC for model with sig preds only is 0.597, earlier it was 0.592
```

```{r, warning=FALSE, echo=FALSE,results='hide',message=FALSE}
kable(ct2)
```

```{r}
library(DescTools)
PseudoR2(mod_new)
```

```{r}
#GOF test
library(glmtoolbox)
hltest(mod_new)
```


```{r, warning=FALSE}
#Creating 3 weight variables

# Define the sampling fractions for each stratum
sampling_fractions <- c(
  'Midwest non-rural' = 0.288,
  'Northeast non-rural' = 0.295,
  'South non-rural' = 0.289,
  'West non-rural' = 0.291,
  'Rural Combined' = 0.287
)

# 1. Probability of selection for each respondent
dat4$prob_selection <- sapply(dat4$stratum_5_categories, function(stratum) sampling_fractions[stratum])

# 2. Expected probability of response for each respondent
dat4$prob_response <- predict(mod_new, newdata=dat4, type = "response")

# 3. Base weight for each respondent
dat4$base_weight <- 1 / dat4$prob_selection

# 4. Nonresponse weight for each respondent
dat4$nonresponse_weight <- 1 / dat4$prob_response

# 5. Raw adjusted weight for each respondent
dat4$raw_adjusted_weight <- dat4$base_weight * dat4$nonresponse_weight
```

```{r, warning=FALSE}
#Creating a dataframe with only the RESPONDERS (Response indicator = Yes)
dat4x <- dat4 %>% 
  filter(Response_indicator2 == 'Yes')
```

**Descriptives of weights for the overall database BEFORE CALIBRATION**
```{r, warning=FALSE}
des_overall <- dat4x %>%
  tbl_summary(#by= "stratum_5_categories",
    include = c(base_weight, nonresponse_weight, raw_adjusted_weight), 
                 type = list(base_weight ~ "continuous", 
                             nonresponse_weight ~ "continuous",
                             raw_adjusted_weight ~ "continuous"),
                 percent = "column",
                 statistic = list(all_continuous() ~ "{min}, {mean}, {median}, ({p1}, {p5}, {p10}, {p90}, {p95}, {p99}), {max}",
                            all_categorical() ~ "{p}"),
                 digits = list(all_continuous() ~ c(1,1),
                               all_categorical() ~ 1),
                 missing = "no")%>%
  modify_header(all_stat_cols() ~ "{level} ({style_percent(p)}%)") %>%
  modify_spanning_header(starts_with("stat_") ~ "For overall") %>%
  #add_p() %>%
  #bold_p() %>% 
  #add_overall() %>% 
  bold_labels() %>% 
  italicize_levels() %>% 
  as_flex_table()

des_overall
```

**Descriptives of weights by stratum BEFORE CALIBRATION**
```{r, warning=FALSE, fig.width=0.2, fig.height=4}
des_st <- dat4x %>%
  tbl_summary(by= "stratum_5_categories",
    include = c(base_weight, nonresponse_weight, raw_adjusted_weight), 
                 type = list(base_weight ~ "continuous", 
                             nonresponse_weight ~ "continuous",
                             raw_adjusted_weight ~ "continuous"),
                 percent = "column",
                 statistic = list(all_continuous() ~ "{min}, {mean}, {median}, ({p1}, {p5}, {p10}, {p90}, {p95}, {p99}), {max}",
                            all_categorical() ~ "{p}"),
                 digits = list(all_continuous() ~ c(1,1),
                               all_categorical() ~ 1),
                 missing = "no")%>%
  modify_header(all_stat_cols() ~ "{level} ({style_percent(p)}%)") %>%
  modify_spanning_header(starts_with("stat_") ~ "By strata") %>%
  #add_p() %>%
  #bold_p() %>% 
  #add_overall() %>% 
  bold_labels() %>% 
  italicize_levels() %>% 
  as_flex_table()
  #flextable::set_table_properties(width = "60%")  # Adjust the width as needed

  # Adjust the width of the flextable
des_st <- flextable::set_table_properties(des_st, width = .2)  # Adjust the width as needed

des_st
```


**Histogram for the weights BEFORE CALIBRATION**
```{r, warning=FALSE}
#par(mfrow=c(1,3))
hist(dat4x$base_weight, main="Base weight", xlab="Base weight")
hist(dat4x$nonresponse_weight, main="Nonresponse weight", xlab="Nonresponse weight")
hist(dat4x$raw_adjusted_weight, main="Raw adjusted weight", xlab="Raw adjusted weight")
```


**Boxplot for the weights BEFORE CALIBRATION**
```{r, warning=FALSE}
par(mfrow=c(1,3))
boxplot(dat4x$base_weight, main="Base weight")
Boxplot(dat4x$nonresponse_weight, main="Nonresponse weight")
Boxplot(dat4x$raw_adjusted_weight, main="Raw adjusted weight")
```


**1+L for raw adjusted weight BEFORE CALIBRATION**

```{r, warning=FALSE}
#computing 1+L for overall data using raw adj weight for respondents only
vif <- dat4x %>%
    summarise(
    mu = mean(raw_adjusted_weight),
    std = sd(raw_adjusted_weight),
    cv = std / mu,
    var_inflation = 1 + cv^2
  )

vif
#kable(vif, caption = "1+L for overall data")
```

```{r, warning=FALSE}
#Grouping the data by stratum for responents only
vif1 <- dat4x %>%
  group_by(stratum_5_categories) %>%
  summarise(
    mu1 = mean(raw_adjusted_weight),
    std1 = sd(raw_adjusted_weight),
    cv1 = std1 / mu1,
    var_inflation1 = 1 + cv1^2
  )

vif1

#kable(vif1, caption = "1+L by stratum")
```

```{r, warning=FALSE}
#*Post Stratification**
library(survey)
```

```{r, warning=FALSE}
#Creating control totals for only respondents

dat5x <- dat4x %>%
  mutate(control_totals = case_when(
    stratum_5_categories == "Midwest non-rural" & teach_hosp2 == "Yes" & mapp182 == "Yes" ~ 'Midwest non-rural-Yes-Yes',
    stratum_5_categories == "Northeast non-rural" & teach_hosp2 == "Yes" & mapp182 == "Yes" ~ 'Northeast non-rural-Yes-Yes',
    stratum_5_categories == "South non-rural" & teach_hosp2 == "Yes" & mapp182 == "Yes" ~ 'South non-rural-Yes-Yes',
    stratum_5_categories == "West non-rural" & teach_hosp2 == "Yes" & mapp182 == "Yes" ~ 'West non-rural-Yes-Yes',
    stratum_5_categories == "Rural combined" & teach_hosp2 == "Yes" & mapp182 == "Yes" ~ 'Rural combined-Yes-Yes',
    stratum_5_categories == "Midwest non-rural" & teach_hosp2 == "No" & mapp182 == "Yes" ~ 'Midwest non-rural-No-Yes',
    stratum_5_categories == "Northeast non-rural" & teach_hosp2 == "No" & mapp182 == "Yes" ~ 'Northeast non-rural-No-Yes',
    stratum_5_categories == "South non-rural" & teach_hosp2 == "No" & mapp182 == "Yes" ~ 'South non-rural-No-Yes',
    stratum_5_categories == "West non-rural" & teach_hosp2 == "No" & mapp182 == "Yes" ~ 'West non-rural-No-Yes',
    stratum_5_categories == "Rural combined" & teach_hosp2 == "No" & mapp182 == "Yes" ~ 'Rural combined-No-Yes',
    stratum_5_categories == "Midwest non-rural" & teach_hosp2 == "Yes" & mapp182 == "No" ~ 'Midwest non-rural-Yes-No',
    stratum_5_categories == "Northeast non-rural" & teach_hosp2 == "Yes" & mapp182 == "No" ~ 'Northeast non-rural-Yes-No',
    stratum_5_categories == "South non-rural" & teach_hosp2 == "Yes" & mapp182 == "No" ~ 'South non-rural-Yes-No',
    stratum_5_categories == "West non-rural" & teach_hosp2 == "Yes" & mapp182 == "No" ~ 'West non-rural-Yes-No',
    stratum_5_categories == "Rural combined" & teach_hosp2 == "Yes" & mapp182 == "No" ~ 'Rural combined-Yes-No',
    stratum_5_categories == "Midwest non-rural" & teach_hosp2 == "No" & mapp182 == "No" ~ 'Midwest non-rural-No-No',
    stratum_5_categories == "Northeast non-rural" & teach_hosp2 == "No" & mapp182 == "No" ~ 'Northeast non-rural-No-No',
    stratum_5_categories == "South non-rural" & teach_hosp2 == "No" & mapp182 == "No" ~ 'South non-rural-No-No',
    stratum_5_categories == "West non-rural" & teach_hosp2 == "No" & mapp182 == "No" ~ 'West non-rural-No-No',
    stratum_5_categories == "Rural combined" & teach_hosp2 == "No" & mapp182 == "No" ~ 'Rural combined-No-No',
    TRUE ~ "Midwest non-rural-No-No"  # This line assigns NA to all other cases
  ))
#dat5$control_totals <- as.factor(dat5$control_totals)
```


```{r, warning=FALSE}
#replacing the frequencies to control totals

# Adding a new row to the dataframe
# If 'control_totals' is not the first column, adjust the position accordingly

new_row <- data.frame(matrix(ncol = 20, nrow = 1)) # Create a new row with 20 columns
colnames(new_row) <- colnames(dat5x) # Make sure column names match
new_row$control_totals <- "Midwest non-rural-Yes-Yes" # Assign the specific value to 'control_totals'

dat5x <- rbind(dat5x, new_row) # Append the new row to dat5x

# Check for missing values in 'control_totals' after adding the new row
#print(sum(is.na(dat5x$control_totals)))

# View the last few rows to confirm the addition
#tail(dat5x)
```


```{r, warning=FALSE}
# Sample from 'Midwest non-rural-Yes-Yes' to reduce to 18 instances
midwest_sample <- dat5x %>%
  dplyr::filter(control_totals == "Midwest non-rural-Yes-Yes") %>%
  sample_n(18, replace = T)

# Sample from 'Northeast non-rural-Yes-Yes' to reduce to 12 instances
northeast_sample <- dat5x %>% 
  filter(control_totals == "Northeast non-rural-Yes-Yes") %>% 
  sample_n(12, replace = T)

# Sample from "South non-rural-Yes-Yes" to reduce to 12 instances
south_sample <- dat5x %>%
 filter(control_totals == "South non-rural-Yes-Yes") %>%
 sample_n(23, replace = T)
 
# Sample from "West non-rural-Yes-Yes" to reduce to 12 instances
west_sample <- dat5x %>%
   filter(control_totals == "West non-rural-Yes-Yes") %>%
   sample_n(35, replace = T)
 
# Sample from "Rural combined-Yes-Yes" to reduce to 12 instances
rural_sample <- dat5x %>%
  filter(control_totals == "Rural combined-Yes-Yes") %>%
  sample_n(70, replace = T)

# Sample from "Midwest non-rural-No-Yes" to reduce to 12 instances
  midwest_no_sample <- dat5x %>%
  filter(control_totals == "Midwest non-rural-No-Yes") %>%
  sample_n(183, replace = T)

# Sample from "Northeast non-rural-No-Yes" to reduce to 12 instances
  northeast_no_sample <- dat5x %>%
    filter(control_totals == "Northeast non-rural-No-Yes") %>%
    sample_n(27, replace = T)

# Sample from "South non-rural-No-Yes" to reduce to 12 instances
  south_no_sample <- dat5x %>%
  filter(control_totals == "South non-rural-No-Yes") %>%
  sample_n(123, replace = T)

# Sample from "West non-rural-No-Yes" to reduce to 12 instances
  west_no_sample <- dat5x %>%
    filter(control_totals == "West non-rural-No-Yes") %>%
      sample_n(90, replace = T)

# Sample from "Rural combined-No-Yes" to reduce to 12 instances
  rural_no_sample <- dat5x %>%
  filter(control_totals == "Rural combined-No-Yes") %>%
  sample_n(757, replace = T)
  
# Sample from "Midwest non-rural-Yes-No" to reduce to 12 instances
  midwest_yes_sample <- dat5x %>%
  filter(control_totals == "Midwest non-rural-Yes-No") %>%
  sample_n(400, replace = T)

# Sample from "Northeast non-rural-Yes-No" to reduce to 12 instances
 northeast_yes_sample <- dat5x %>%
 filter(control_totals == "Northeast non-rural-Yes-No") %>%
 sample_n(338, replace = T)
 
# Sample from "South non-rural-Yes-No" to reduce to 12 instances
 south_yes_sample <- dat5x %>%
 filter(control_totals == "South non-rural-Yes-No") %>%
 sample_n(597, replace = T)
 
# Sample from "West non-rural-Yes-No" to reduce to 12 instances
 west_yes_sample <- dat5x %>%
   filter(control_totals == "West non-rural-Yes-No") %>%
   sample_n(370, replace = T)
 
# Sample from "Rural combined-Yes-No" to reduce to 12 instances
  rural_yes_sample <- dat5x %>%
  filter(control_totals == "Rural combined-Yes-No") %>%
  sample_n(42, replace = T)
  
# Sample from "Midwest non-rural-No-No" to reduce to 12 instances
midwest_no_no_sample <- dat5x %>%
  dplyr::filter(control_totals == "Midwest non-rural-No-No") %>%
  sample_n(407, replace = T)

# Sample from "Northeast non-rural-No-No" to reduce to 12 instances
  northeast_no_no_sample <- dat5x %>%
    filter(control_totals == "Northeast non-rural-No-No") %>%
    sample_n(97, replace = T)

# sample from "South non-rural-No-No" to reduce to 12 instances
  south_no_no_sample <- dat5x %>%
  filter(control_totals == "South non-rural-No-No") %>%
  sample_n(347, replace = T)
  
# sample from "West non-rural-No-No" to reduce to 12 instances
  west_no_no_sample <- dat5x %>%
    filter(control_totals == "West non-rural-No-No") %>%
      sample_n(209, replace = T)

# Sample from "Rural combined-No-No" to reduce to 12 instances
  rural_no_no_sample <- dat5x %>%
  filter(control_totals == "Rural combined-No-No") %>%
  sample_n(176, replace = T)  



# Bind the rest of the data that does not need to change
rest_of_data <- dat5x %>% 
  filter(!(control_totals %in% c("Midwest non-rural-Yes-Yes", "Northeast non-rural-Yes-Yes", "South non-rural-Yes-Yes", "West non-rural-Yes-Yes", "Rural combined-Yes-Yes", "Midwest non-rural-No-Yes", "Northeast non-rural-No-Yes", "South non-rural-No-Yes", "West non-rural-No-Yes", "Rural combined-No-Yes", "Midwest non-rural-Yes-No", "Northeast non-rural-Yes-No", "South non-rural-Yes-No", "West non-rural-Yes-No", "Rural combined-Yes-No", "Midwest non-rural-No-No", "Northeast non-rural-No-No", "South non-rural-No-No", "West non-rural-No-No", "Rural combined-No-No")))

# Combine all parts back into a single dataframe
dat6x <- bind_rows(midwest_sample, northeast_sample, rest_of_data, south_sample, west_sample, rural_sample, midwest_no_sample, northeast_no_sample, south_no_sample, west_no_sample, rural_no_sample, midwest_yes_sample, northeast_yes_sample, south_yes_sample, west_yes_sample, rural_yes_sample, midwest_no_no_sample, northeast_no_no_sample, south_no_no_sample, west_no_no_sample, rural_no_no_sample)

# Verify the changes
as.data.frame(print(table(dat6x$control_totals)))
```



```{r, warning=FALSE}
#taking only the completed cases
dat7x <- dat6x %>% 
          filter(complete.cases(.))
    
```


```{r, warning=FALSE}
#*Post Stratification**

#Creating a survey design object
design <- svydesign(ids = ~sample_id, weights = ~raw_adjusted_weight, data = dat4x)
```

```{r, warning=FALSE}
#Pop totals
nps <- xtabs(~stratum_5_categories + teach_hosp2 + mapp182, data = dat7x)
#as.data.frame(nps)
```

```{r, warning=FALSE}
#postratification
calibrated_design <- postStratify(design,
                                  strata = ~stratum_5_categories + teach_hosp2 + mapp182,
                                  population = nps)
```

```{r, warning=FALSE}
summary(calibrated_design)
```

```{r, warning=FALSE}
svytotal(~interaction(stratum_5_categories, teach_hosp2, mapp182), calibrated_design)
```

```{r}
dat4x$calibrated_weights <- weights(calibrated_design)

```

**Descriptives of weights for the overall database of RESPONDENTS only AFTER CALIBRATION**
```{r, warning=FALSE}
des_overall_calib <- survey::svydesign(ids=~sample_id, weights = ~ calibrated_weights, strata = ~stratum_5_categories,  data=dat4x, nest = T) %>% 
  tbl_svysummary(#by= "stratum_5_categories",
    include = c(base_weight, nonresponse_weight, raw_adjusted_weight), 
                 type = list(base_weight ~ "continuous", 
                             nonresponse_weight ~ "continuous",
                             raw_adjusted_weight ~ "continuous"),
                 percent = "column",
                 statistic = list(all_continuous() ~ "{min}, {mean}, {median}, ({p1}, {p5}, {p10}, {p90}, {p95}, {p99}), {max}",
                            all_categorical() ~ "{p}"),
                 digits = list(all_continuous() ~ c(1,1),
                               all_categorical() ~ 1),
                 missing = "no")%>%
  modify_header(all_stat_cols() ~ "{level} ({style_percent(p)}%)") %>%
  #add_p() %>%
  #bold_p() %>% 
  #add_overall() %>% 
  bold_labels() %>% 
  italicize_levels() %>% 
  as_flex_table()

des_overall_calib
```


**Descriptives of weights by stratum of RESPONDENTS only AFTER CALIBRATION**
```{r}
#descriptives of the weights by each stratum
des_st_calib <- 
 survey::svydesign(ids=~sample_id, weights = ~ calibrated_weights, strata = ~stratum_5_categories,  data=dat4x, nest = T) %>% 
  tbl_svysummary(by= "stratum_5_categories",
    include = c(base_weight, nonresponse_weight, raw_adjusted_weight), 
                 type = list(base_weight ~ "continuous", 
                             nonresponse_weight ~ "continuous",
                             raw_adjusted_weight ~ "continuous"),
                 percent = "column",
                 statistic = list(all_continuous() ~ "{min}, {mean}, {median}, ({p1}, {p5}, {p10}, {p90}, {p95}, {p99}), {max}",
                            all_categorical() ~ "{p}"),
                 digits = list(all_continuous() ~ c(1,1),
                               all_categorical() ~ 1),
                 missing = "no")%>%
  #modify_header(all_stat_cols() ~ "{level} ({style_percent(p)}%)") %>%
  modify_header(update = list(label ~ "",
                              stat_1 ~ "**Midwest non-rural** (n = 125)",
                              stat_2 ~ "**Northeast non-rural** (n = 73)",
                              stat_3 ~ "**Rural combined** (n = 163)",
                              stat_4 ~ "**South non-rural** (n = 139)",
                              stat_5 ~ "**West non-rural** (n = 106)"
                              ))%>%
  modify_spanning_header(starts_with("stat_") ~ "For overall") %>%
  #add_p() %>%
  #bold_p() %>% 
  #add_overall() %>% 
  bold_labels() %>% 
  italicize_levels() %>% 
  as_flex_table()

des_st_calib
```


**Histogram for the weights AFTER CALIBRATION**
```{r, warning=FALSE}
par(mfrow=c(1,3))
hist(dat4x$base_weight, main="Base weight", weights=dat4x$calibrated_weights)
hist(dat7x$nonresponse_weight, main="Nonresponse weight", weights=dat4x$calibrated_weights)
hist(dat7x$raw_adjusted_weight, main="Raw adjusted weight", weights=dat4x$calibrated_weights)
```
<br>
**Boxplot for the weights AFTER CALIBRATION**
```{r, warning=FALSE}
par(mfrow=c(1,3))
boxplot(dat7x$base_weight, main="Base weight", weights=dat4x$calibrated_weights)
Boxplot(dat7x$nonresponse_weight, main="Nonresponse weight", weights=dat4x$calibrated_weights)
Boxplot(dat7x$raw_adjusted_weight, main="Raw adjusted weight", weights=dat4x$calibrated_weights)
```


**Variance of inflation AFTER CALIBRATION**
```{r, warning=FALSE}
#computing 1+L for overall data using raw adj weight for respondents only
vif_c1 <- dat4x %>%
    summarise(
    mu = mean(calibrated_weights),
    std = sd(calibrated_weights),
    cv = std / mu,
    var_inflation = 1 + cv^2
  )

library(knitr)
knitr::kable(vif_c1, format = "markdown", caption = "1+L for overall data")
```

```{r, warning=FALSE}
#Grouping the data by stratum for responents only
vif2 <- dat4x %>%
  group_by(stratum_5_categories) %>%
  summarise(
    mu1 = mean(calibrated_weights),
    std1 = sd(calibrated_weights),
    cv1 = std1 / mu1,
    var_inflation1 = 1 + cv1^2
  )

kable(vif2, caption = "1+L by stratum")
```



**Sum of weights AFTER CALIBRATION**
```{r, warning=FALSE}
sum(dat4x$base_weight)
sum(dat7x$nonresponse_weight)
```

```{r, warning=FALSE}
#sum of raw adj weight before calibration
sum(dat4x$raw_adjusted_weight)

#sum of raw adj weight after calibration
sum(dat7x$raw_adjusted_weight)


sum(weights(design))
sum(weights(calibrated_design))
```

**Number of respondents for the 20 classes BEFORE CALIBRATION**
```{r, warning=FALSE}
library(flextable)
# Original data summarization with interaction variable
summary_table <- dat4x %>%
  mutate(interaction_var = interaction(teach_hosp2, mapp182)) %>%
  group_by(stratum_5_categories, interaction_var) %>%
  summarise(count = n(), .groups = 'drop')

# Calculate row totals
row_totals <- summary_table %>%
  group_by(stratum_5_categories) %>%
  summarise(count = sum(count)) %>%
  mutate(interaction_var = "Total")

# Append row totals to the summary
summary_with_row_totals <- bind_rows(summary_table, row_totals)

# Pivot to wide format including row totals
wide_table_with_row_totals <- summary_with_row_totals %>%
  pivot_wider(names_from = interaction_var, values_from = count, values_fill = list(count = 0))

# Calculate column totals (this includes the previously calculated row totals as part of the calculation)
column_totals <- wide_table_with_row_totals %>%
  summarise(across(-stratum_5_categories, sum, na.rm = TRUE)) %>%
  mutate(stratum_5_categories = "Total")

# Combine wide table with column totals
final_table_with_column_totals <- bind_rows(wide_table_with_row_totals, column_totals)

ft <- flextable(final_table_with_column_totals) %>%
  set_table_properties(width = .5, layout = "autofit") %>%
  align(align = "center", part = "all") %>%
  set_header_labels(
    `stratum_5_categories` = "Stratum",
    `No.Yes` = "Teaching Hospital=N x Critical Access Hospital=Y",
    `Yes.No` = "Teaching Hospital=Y  x Critical Access Hospital=N",
    `No.No` = "Teaching Hospital=N x Critical Access Hospital=N",
    `Yes.Yes` = "Teaching Hospital=Y x Critical Access Hospital=Y",
    `Total` = "Total"
  ) %>%
  set_caption("Crosstable for Teaching and Critical hospitals by Stratum")

ft

```

**Number of respondents for the 20 classes AFTER CALIBRATION**
```{r, warning=FALSE}
library(flextable)
# Original data summarization with interaction variable
summary_table1 <- dat7x %>%
  mutate(interaction_var = interaction(teach_hosp2, mapp182)) %>%
  group_by(stratum_5_categories, interaction_var) %>%
  summarise(count = n(), .groups = 'drop')

# Calculate row totals
row_totals1 <- summary_table1 %>%
  group_by(stratum_5_categories) %>%
  summarise(count = sum(count)) %>%
  mutate(interaction_var = "Total")

# Append row totals to the summary
summary_with_row_totals1 <- bind_rows(summary_table1, row_totals1)

# Pivot to wide format including row totals
wide_table_with_row_totals1 <- summary_with_row_totals1 %>%
  pivot_wider(names_from = interaction_var, values_from = count, values_fill = list(count = 0))

# Calculate column totals (this includes the previously calculated row totals as part of the calculation)
column_totals1 <- wide_table_with_row_totals1 %>%
  summarise(across(-stratum_5_categories, sum, na.rm = TRUE)) %>%
  mutate(stratum_5_categories = "Total")

# Combine wide table with column totals
final_table_with_column_totals1 <- bind_rows(wide_table_with_row_totals1, column_totals1)

ft1 <- flextable(final_table_with_column_totals1) %>%
  set_table_properties(width = .5, layout = "autofit") %>%
  align(align = "center", part = "all") %>%
  set_header_labels(
    `stratum_5_categories` = "Stratum",
    `No.Yes` = "Teaching Hospital=N x Critical Access Hospital=Y",
    `Yes.No` = "Teaching Hospital=Y  x Critical Access Hospital=N",
    `No.No` = "Teaching Hospital=N x Critical Access Hospital=N",
    `Yes.Yes` = "Teaching Hospital=Y x Critical Access Hospital=Y",
    `Total` = "Total"
  ) %>%
  set_caption("Crosstable for Teaching and Critical hospitals by Stratum after Calibration")

ft1

```




##########################################################################
# *CREATING 13 UNIQUE STRATA*
##########################################################################
**13 unique strata for sample**

```{r, warning=FALSE}
dat4x$midwest_non_rural_CA <- factor(
  ifelse(dat4x$stratum_5_categories=="Midwest non-rural" & dat4x$mapp182=="Yes", "Yes", "No"))

dat4x$rural_combined_CA <- factor(
  ifelse(dat4x$stratum_5_categories=="Rural combined" & dat4x$mapp182=="Yes", "Yes", "No"))

dat4x$west_non_rural_CA <- factor(
  ifelse(dat4x$stratum_5_categories=="West non-rural" & dat4x$mapp182=="Yes", "Yes", "No"))

dat4x$eastcoast_non_rural <- factor(
  ifelse(dat4x$stratum_5_categories=="Northeast non-rural" & dat4x$mapp182=="Yes", "Yes",
  ifelse(dat4x$stratum_5_categories=="South non-rural" & dat4x$mapp182=="Yes", "Yes", "No")))

dat4x$midwest_non_rural_TH <- factor(
  ifelse(dat4x$stratum_5_categories=="Midwest non-rural" & dat4x$mapp182=="No" & dat4x$teach_hosp2=="Yes", "Yes", "No"))

dat4x$northeast_non_rural_TH <- factor(
  ifelse(dat4x$stratum_5_categories=="Northeast non-rural" & dat4x$mapp182=="No" & dat4x$teach_hosp2=="Yes", "Yes", "No"))

dat4x$south_non_rural_TH <- factor(
  ifelse(dat4x$stratum_5_categories=="South non-rural" & dat4x$mapp182=="No" & dat4x$teach_hosp2=="Yes", "Yes", "No"))

dat4x$west_non_rural_TH <- factor(
  ifelse(dat4x$stratum_5_categories=="West non-rural" & dat4x$mapp182=="No" & dat4x$teach_hosp2=="Yes", "Yes", "No"))

dat4x$midwest_non_rural <- factor(
  ifelse(dat4x$stratum_5_categories=="Midwest non-rural" & dat4x$mapp182=="No" & dat4x$teach_hosp2=="No", "Yes", "No"))

dat4x$northeast_non_rural <- factor(
  ifelse(dat4x$stratum_5_categories=="Northeast non-rural" & dat4x$mapp182=="No" & dat4x$teach_hosp2=="No", "Yes", "No"))

dat4x$south_non_rural <- factor(
  ifelse(dat4x$stratum_5_categories=="South non-rural" & dat4x$mapp182=="No" & dat4x$teach_hosp2=="No", "Yes", "No"))

dat4x$west_non_rural <- factor(
  ifelse(dat4x$stratum_5_categories=="West non-rural" & dat4x$mapp182=="No" & dat4x$teach_hosp2=="No", "Yes", "No"))

dat4x$rural_combined <- factor(
  ifelse(dat4x$stratum_5_categories=="Rural combined" & dat4x$teach_hosp2 == "Yes" & dat4x$mapp182=="No", "Yes",
  ifelse(dat4x$stratum_5_categories=="Rural combined" & dat4x$teach_hosp2 == "No" & dat4x$mapp182=="No", "Yes", "No")))
```

```{r, warning=FALSE}
dat4x <- dat4x %>%
        mutate(control_totals = case_when(
                                    dat4x$midwest_non_rural_CA == "Yes" ~ "Midwest non-rural_CA=Y",
                                    dat4x$rural_combined_CA == "Yes" ~ "Rural combined_CA=Y",
                                    dat4x$west_non_rural_CA == "Yes" ~ "West non-rural_CA=Y", 
                                    dat4x$eastcoast_non_rural == "Yes" ~ "Eastcoast non-rural_CA=Y",
                                    dat4x$midwest_non_rural_TH == "Yes" ~ "Midwest_non_rural_TH=Y,CA=N",
                                    dat4x$northeast_non_rural_TH == "Yes" ~ "Northeast non-rural_CA=N, TH=Y",
                                    dat4x$south_non_rural_TH == "Yes" ~ "South non-rural_CA=N, TH=Y",
                                    dat4x$west_non_rural_TH == "Yes" ~ "West non-rural_CA=Y, TH=Y",
                                    dat4x$midwest_non_rural == "Yes" ~ "Midwest non-rural_CA=N, TH=N",
                                    dat4x$northeast_non_rural == "Yes" ~ "Northeast non-rural_CA=N, TH=N",
                                    dat4x$south_non_rural == "Yes" ~ "South non-rural_CA=N, TH=N", 
                                    dat4x$west_non_rural == "Yes" ~ "West non-rural_CA=N, TH=N", 
                                    dat4x$rural_combined == "Yes" ~ "Rural combined-Rural not CA",
                                    TRUE ~ NA))
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
# samp13 <- as.data.frame(table(dat4x$control_totals))
# 
# library(knitr)
# knitr::kable(samp13, format = "markdown")
```

**13 unique strata for population**

```{r, warning=FALSE}
#Replace survey sample with population data

midwest_non_rural_CA_sample <- dat4x %>%
  dplyr::filter(control_totals == "Midwest non-rural_CA=Y") %>%
  sample_n(201, replace = T)

rural_combined_CA_sample <- dat4x %>%
  filter(control_totals == "Rural combined_CA=Y") %>%
  sample_n(827, replace = T)
 
west_non_rural_CA_sample <- dat4x %>%
   filter(control_totals == "West non-rural_CA=Y") %>%
   sample_n(125, replace = T)
 
eastcoast_non_rural_CA_sample <- dat4x %>% 
  filter(control_totals == "Eastcoast non-rural_CA=Y") %>%
  sample_n(185, replace = T)

midwest_non_rural_TH_sample <- dat4x %>% 
  filter(control_totals == "Midwest_non_rural_TH=Y,CA=N") %>%
  sample_n(400, replace = T)

northeast_non_rural_TH_sample <- dat4x %>%
  filter(control_totals == "Northeast non-rural_CA=N, TH=Y") %>%
  sample_n(338, replace = T)

south_non_rural_TH_sample <- dat4x %>%
  filter(control_totals == "South non-rural_CA=N, TH=Y") %>%
  sample_n(597, replace = T)

west_non_rural_TH_sample <- dat4x %>% 
  filter(control_totals == "West non-rural_CA=Y, TH=Y") %>%
  sample_n(370, replace = T)

midwest_non_rural_sample <- dat4x %>% 
  filter(control_totals == "Midwest non-rural_CA=N, TH=N") %>%
  sample_n(407, replace = T)

northeast_non_rural_sample <- dat4x %>%
  filter(control_totals == "Northeast non-rural_CA=N, TH=N") %>%
  sample_n(97, replace = T)

south_non_rural_sample <- dat4x %>% 
  filter(control_totals == "South non-rural_CA=N, TH=N") %>%
  sample_n(347, replace = T)

west_non_rural_sample <- dat4x %>%
  filter(control_totals == "West non-rural_CA=N, TH=N") %>%
  sample_n(209, replace = T)

rural_combined_sample <- dat4x %>%
  filter(control_totals == "Rural combined-Rural not CA") %>%
  sample_n(218, replace = T)


# Bind the rest of the data that does not need to change
rest_of_data <- dat4x %>% 
  filter(!(control_totals %in% c("Midwest non-rural_CA=Y", "Rural combined_CA=Y", "West non-rural_CA=Y", "Eastcoast non-rural_CA=Y", "Midwest_non_rural_TH=Y,CA=N", "Northeast non-rural_CA=N, TH=Y", "South non-rural_CA=N, TH=Y", "West non-rural_CA=Y, TH=Y", "Midwest non-rural_CA=N, TH=N", "Northeast non-rural_CA=N, TH=N", "South non-rural_CA=N, TH=N", "West non-rural_CA=N, TH=N", "Rural combined-Rural not CA")))


# Combine all parts back into a single dataframe
dat6x <- bind_rows(midwest_non_rural_CA_sample, rural_combined_CA_sample, west_non_rural_CA_sample, eastcoast_non_rural_CA_sample, midwest_non_rural_TH_sample, northeast_non_rural_TH_sample, south_non_rural_TH_sample, west_non_rural_TH_sample, midwest_non_rural_sample, northeast_non_rural_sample, south_non_rural_sample, west_non_rural_sample, rural_combined_sample, rest_of_data)

# Verify the changes
#table(dat6x$control_totals)
```


```{r, warning=FALSE, echo=FALSE, results=FALSE}
# pop13 <- as.data.frame(table(dat6x$control_totals))
# 
# knitr::kable(pop13, format = "markdown")
```

##########################################################################
# *AFTER CREATING 13 STRATA*
##########################################################################


```{r, warning=FALSE}
#*Post Stratification**
design <- svydesign(ids = ~sample_id, weights = ~raw_adjusted_weight, data = dat4x)
```

```{r, warning=FALSE}
#Pop totals
nps <- xtabs(~control_totals + teach_hosp2 + mapp182, data = dat6x)
#as.data.frame(nps)
```

```{r, warning=FALSE}
#postratification
calibrated_design <- postStratify(design,
                                  strata = ~control_totals + teach_hosp2 + mapp182,
                                  population = nps)
```

```{r, warning=FALSE}
summary(calibrated_design)
```

```{r, warning=FALSE}
svytotal(~interaction(control_totals, teach_hosp2, mapp182), calibrated_design)
```

*****************

#creating calibrated_weight as a variable
```{r}
dat4x$calibrated_weights <- weights(calibrated_design)

```
**************

**Descriptives of weights for the overall database after creating 13 unique strata** 
```{r, warning=FALSE}
des_overall_calib <- survey::svydesign(ids=~sample_id, weights = ~ calibrated_weights, strata = ~stratum_5_categories,  data=dat4x, nest = T) %>% 
  tbl_svysummary(#by= "stratum_5_categories",
    include = c(base_weight, nonresponse_weight, raw_adjusted_weight), 
                 type = list(base_weight ~ "continuous", 
                             nonresponse_weight ~ "continuous",
                             raw_adjusted_weight ~ "continuous"),
                 percent = "column",
                 statistic = list(all_continuous() ~ "{min}, {mean}, {median}, ({p1}, {p5}, {p10}, {p90}, {p95}, {p99}), {max}",
                            all_categorical() ~ "{p}"),
                 digits = list(all_continuous() ~ c(1,1),
                               all_categorical() ~ 1),
                 missing = "no")%>%
  modify_header(all_stat_cols() ~ "{level} ({style_percent(p)}%)") %>%
  #add_p() %>%
  #bold_p() %>% 
  #add_overall() %>% 
  bold_labels() %>% 
  italicize_levels() %>% 
  as_flex_table()

des_overall_calib
```


**Descriptives of weights by 13 strata of RESPONDENTS**
```{r}
#descriptives of the weights by each stratum
des_st_calib <- 
 survey::svydesign(ids=~sample_id, weights = ~ calibrated_weights, strata = ~stratum_5_categories,  data=dat4x, nest = T) %>% 
  tbl_svysummary(by= "control_totals",
    include = c(base_weight, nonresponse_weight, raw_adjusted_weight), 
                 type = list(base_weight ~ "continuous", 
                             nonresponse_weight ~ "continuous",
                             raw_adjusted_weight ~ "continuous"),
                 percent = "column",
                 statistic = list(all_continuous() ~ "{min}, {mean}, {median}, ({p1}, {p5}, {p10}, {p90}, {p95}, {p99}), {max}",
                            all_categorical() ~ "{p}"),
                 digits = list(all_continuous() ~ c(1,1),
                               all_categorical() ~ 1),
                 missing = "no")%>%
  modify_header(all_stat_cols() ~ "{level} ({style_percent(p)}%)") %>%
  # modify_header(update = list(label ~ "",
  #                             stat_1 ~ "**Midwest non-rural** (n = 125)",
  #                             stat_2 ~ "**Northeast non-rural** (n = 73)",
  #                             stat_3 ~ "**Rural combined** (n = 163)",
  #                             stat_4 ~ "**South non-rural** (n = 139)",
  #                             stat_5 ~ "**West non-rural** (n = 106)"
  #                             ))%>%
  modify_spanning_header(starts_with("stat_") ~ "For overall") %>%
  #add_p() %>%
  #bold_p() %>% 
  #add_overall() %>% 
  bold_labels() %>% 
  italicize_levels() %>% 
  as_flex_table()

des_st_calib
```
****************


**1+L for uncalibrated and calibrated weights**

```{r, warning=FALSE}
#Grouping the data by stratum for responents only
vif1_13 <- dat4x %>%
  group_by(control_totals) %>%
  summarise(
    mu1 = mean(raw_adjusted_weight),
    std1 = sd(raw_adjusted_weight),
    cv1 = std1 / mu1,
    var_inflation1 = 1 + cv1^2
  )

library(knitr)
kable(vif1_13, caption = "1+L by 13 strata for uncalibrated weight")
```

```{r, warning=FALSE}
#Grouping the data by stratum for responents only
vif1_13w <- dat4x %>%
  group_by(control_totals) %>%
  summarise(
    mu1 = mean(calibrated_weights),
    std1 = sd(calibrated_weights),
    cv1 = std1 / mu1,
    var_inflation1 = 1 + cv1^2
  )

vif1_13w
kable(vif1_13w, caption = "1+L by 13 strata for calibrated weight")
```

**Sum of weights**
```{r}
sum(dat6x$base_weight)
sum(dat6x$nonresponse_weight)
sum(dat6x$raw_adjusted_weight)
sum(weights(design))
sum(weights(calibrated_design))
```

**Checking for the match of the control totals in each post-stratum**
```{r}
#Midwest non-rural_CA=Y
table(dat6x$midwest_non_rural_CA)
svytotal(~midwest_non_rural_CA, calibrated_design)

#Rural combined_CA=Y
table(dat6x$rural_combined_CA)
svytotal(~rural_combined_CA, calibrated_design)

#West non-rural_CA=Y
table(dat6x$west_non_rural_CA)
svytotal(~west_non_rural_CA, calibrated_design)

#Eastcoast non-rural_CA=Y
table(dat6x$eastcoast_non_rural)
svytotal(~eastcoast_non_rural, calibrated_design)

#Midwest_non_rural_TH=Y,CA=N
table(dat6x$midwest_non_rural_TH)
svytotal(~midwest_non_rural_TH, calibrated_design)

#Northeast non-rural_CA=N, TH=Y
table(dat6x$northeast_non_rural_TH)
svytotal(~northeast_non_rural_TH, calibrated_design)

#South non-rural_CA=N, TH=Y
table(dat6x$south_non_rural_TH)
svytotal(~south_non_rural_TH, calibrated_design)

#West non-rural_CA=Y, TH=Y
table(dat6x$west_non_rural_TH)
svytotal(~west_non_rural_TH, calibrated_design)

#Midwest non-rural_CA=N, TH=N
table(dat6x$midwest_non_rural)
svytotal(~midwest_non_rural, calibrated_design)

#Northeast non-rural_CA=N, TH=N
table(dat6x$northeast_non_rural)
svytotal(~northeast_non_rural, calibrated_design)

#South non-rural_CA=N, TH=N
table(dat6x$south_non_rural)
svytotal(~south_non_rural, calibrated_design)

#West non-rural_CA=N, TH=N
table(dat6x$west_non_rural)
svytotal(~west_non_rural, calibrated_design)

#Rural combined-Rural not CA
table(dat6x$rural_combined)
svytotal(~rural_combined, calibrated_design)
```
Summing up **Yes** for each of the 13 strata gives a total of 4312 which matches the control totals.


#merging with original data for checking 1+L
```{r}
datnew3 <- merge(datA, dat4x, by="sample_id")
```

```{r, warning=FALSE}
#with merged sample data

vif_overall2 <- datnew3 %>%
    summarise(
    mu = mean(calibrated_weights),
    std = sd(calibrated_weights),
    cv = std / mu,
    var_inflation = 1 + cv^2
  )
vif_overall2
```

```{r}
finaldataFeb16 <- dat4x %>% 
  dplyr::select(sample_id, aha_id, control_totals, base_weight, nonresponse_weight, raw_adjusted_weight, calibrated_weights)
```

```{r}
write.csv(finaldataFeb16, "C:/Users/ilmul/Documents/UMICH/RA works/CHOP Nonresponse weights Winter 2024/final dataFeb16.csv", row.names = FALSE)
```






